---
output: 
  github_document:
    df_print: tibble
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# geoscidata

The goal of geoscidata is to provide interesting and relevant datasets for geoscientists learning R.

## Installation

You can install geoscidata from GitHub using:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/geoscidata")
```

If you can load the without errors, you've installed it correctly!

```{r}
library(geoscidata)
```

## The `warwick` dataset

This dataset is a data frame of rock samples collected in multiple field seasons by the Nova Scotia Department of Energy and Mines in the Warwick Mountain area of Nova Scotia, Canada. It contains qualitative information about rock types, as well as pXRF-measured geochemistry. For more information, see the [dataset download page](https://novascotia.ca/natr/meb/download/dp505.asp).

```{r example}
warwick
```

Some examples of this dataset and ggplot2 include plotting the locations:

```{r warwick-locs}
library(ggplot2)
ggplot(warwick) +
  geom_point(aes(x = longitude, y = latitude, col = date_sampled))
```

Plotting the chemical content by rock type:

```{r warwick-chemgroups, warning=FALSE}
ggplot(warwick) +
  geom_boxplot(aes(x = rock_name, y = Ti_ppm))
```

Plotting relationships between chemical components by rock type:

```{r warwick-chem-scatter-facet, warning=FALSE}
ggplot(warwick) +
  geom_point(aes(x = Pb_ppm, y = Ti_ppm, col = rock_type)) +
  facet_wrap(vars(rock_group)) +
  scale_x_log10() +
  scale_y_log10()
```
